### 2021-03-29 Chapter-3/Chapter-3.tex
Updates from Overleaf

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory.

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

>>>>

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple Cores, each core has two private level-1 (L1) cache, an instruction cache (iCache) and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache make it possible CPUs to fetch the code and data simultaneously and improve the performance. Followed by the level-1 cache, each core also has the unified private level-2 cache. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy. 
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

The current computer memory hierarchy opens the way for side-channel attacks from two aspects. First, the architecture relies on the system software to manage the addressing, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX). Second, the size of the cache is smaller than the main memory, which makes it possible that several program shares the same cache unit (e.g., cache line, cache set).

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_address}
\end{figure}
